The pollination trade-off

### 2018-03-01 publication/supp_info.Rmd
Improve model results figure in supp info

```{r fig-model-results, fig.height = 3, fig.cap = "Model coefficients"}
loadd(tidied_fixed)

tidied_fixed %>%
  filter(term != "(Intercept)" #, 
         # var_trans == 'log'
         ) %>%
  group_by(pollen_category,scale, model, var_trans, term) %>%
  summarise(estimate = first(estimate)) %>%
  group_by() %>%
  humanize() %>%
  ggplot(aes(x = estimate, 
             colour = pollen_category)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(# alpha = 0.25,
               position = position_identity(),
               draw_quantiles = c(0.5, 0.95, 0.05), 
               trim = F, 
               scale = "count",
               binwidth = 0.05, 
               geom = "line") +
  pub_theme() +
  facet_grid(scale ~ term + var_trans, scales = "free_x") +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

>>>>

```{r fig-model-results, fig.height = 3.5, fig.cap = "Model coefficients"}
loadd(tidied_fixed, sites)

tidied_fixed %>%
  filter(term != "(Intercept)" , 
         var_trans == 'log'
         # scale == "community"
         ) %>%
  group_by(pollen_category,scale, model, var_trans, term) %>%
  summarise(estimate = first(estimate)) %>%
  group_by() %>%
  humanize() %>%
  ggplot(aes(x = estimate, 
             colour = pollen_category, 
             fill = pollen_category)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  stat_density(geom = 'area',
               alpha = 0.15,
               position = position_identity(),
               draw_quantiles = c(0.5, 0.95, 0.05), 
               trim = F, 
               scale = "count",
               bins = 15) +
  pub_theme() +
  facet_grid(scale ~ term, scales = "free_x", space = "free_x") +
  scale_color_manual(values = colour_scale_values) +
  scale_fill_manual(values = colour_scale_values) +
  scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
  theme(legend.position = "top") +
  labs(colour = "", fill = "")
```
